---
title: "Evaluating Data-table"
output: html_notebook
---

Is it all it's cracked up to be?  Let's see if it handles factors better than Phaser for a CSV.  

```{r}
library(data.table)
fool<- list.files("C:/GAFCP/SA_Database/Self-Assessments")

folders<- list.files(paste("C:/GAFCP/SA_Database/Self-Assessments/",fool,sep=""),full.names=T)
fsav<- grep("\\.sav",folders)
ffsav <- folders[fsav]
ffsav
```

```{r}
test1 <- Phaser(ffsav[5])
```
```{r}
write.table(test1,"C:/GAFCP/SA_Database/Self-Assessments/2005 Self-assessment/Q15-05.csv",sep=",")
```
Test 1 table has been written out as a csv let's see how data table handles it.  
```{r}
vroom <- fread("C:/GAFCP/SA_Database/Self-Assessments/2005 Self-assessment/Q15-05.csv")
str(vroom)
```

Interesting.  To its credit, it dealt well with the character vector and read the table quickly.

```{r}
pos<- Phaser("C:/GAFCP/SA_Database/Self-Assessments/2005 Self-assessment/Q15-05.csv")
```

Ah, but so did Phaser - looks like it performs fine when the file is a csv.  Does table even handle sav files probably not.

```{r}
test2 <- fread(ffsav[5])
```

Hah, yeah real hard time with the sav file.  

Well one more thing: If I wrap my Phaser command for Savs around Data table instead of data frame does it come out any different.  Let's try the Phaser bank with the as.data.table command

```{r}

PhaserBank<- function(fp) {
  psav<- grep("\\.sav",fp)
  pcsv<- grep("\\.csv",fp)
  pdbf<- grep("\\.dbf",fp)
  dval<- if (length(psav)>0) {library(memisc) 
    library(data.table)
    as.data.table(as.data.set(spss.system.file(fp),stringsAsFactors=F))}
    if (length(psav)>0) return(dval)
  cval<-   if (length(pcsv)>0) (read.csv(fp,sep=",",header=T,as.is=T))
    if (length(pcsv)>0) return(cval)
  dbfl<- if (length(pdbf>0)) {library(foreign)
    read.dbf(fp,as.is=T)}
    if (length(pdbf)>0) return(dbfl)
}
```
```{r}
testbank <- PhaserBank(ffsav[5])
str(testbank)
```

Wow that came out looking pretty fancy.  Automatic coercion to character vectors indeed! I wonder if this will make my melting operations any easier?  


**EVALUATION PASSED!**:  Examining data table documentation for other potentially useful features.

Auto-Merge
===============

If this works I'll be a happy camper.

```{r}
f6 <- PhaserBank(ffsav[6])
mty<- merge(testbank,f6, by="county",all.x=T,all.y=T)
str(mty)
```

Now this is more like it!   As long as all.x And ALL.y=T we're golden.  So this may make the horizontal joins easier.  

