---
title: "Interactive_Census_Scan"
output: html_notebook
---

Trying to create a census scanner script which accepts interactive input from the user.  For example ,search the census database for "race".  Found 11 tables:
1  TABLE DESCRIPTION
2  TABLE DESC...... ETC.

Which of the following?  (Accepts 1:19, all, etc. as input from the user)
takes user input and proceeds with request

Playing around with tips from this link [here](http://stackoverflow.com/questions/3935288/how-to-include-interactive-input-in-script-to-be-run-from-the-command-line).  

SUCCESS!
==============

```{r}
#Attempting

  cat("Please select:  ")
  x <- readLines(file("stdin"),1)
  print(x)
#As a function this did prompt with cat and opened a connection but there was no way I could see to terminate connection.  
```

```{r}
yike <- function() {
  
cat("Hello mate!") 
  x <- readLines(con=stdin(),1)
  print(x)
}

yike()
```

Excellent!  This returns the printed response from the keyboard and can be used for the interactive script! 
