---
title: "Sampling"
output: html_notebook
---





```{r}

population <- rnorm(4000)
msample <- function(pop,nsamples,sampsize) {
  x <- seq(1,nsamples,by=1)
  xr <- rep(0,nsamples)
  for (i in x) {
    xr[i] <- mean(sample(pop,sampsize))
  }
  xr
}

testm <- msample(population,1000,250)


```

Succesful run

```{r}
testm
```

```{r}
library(ggplot2)
qplot(testm)
```

```{r}
test500 <- msample(population,1000,500)
test750 <- msample(population,1000,750)
```

Set up data frame
```{r}
def <- data.frame(m250=testm,
  m500=test500,
  m750=test750)
str(def)
```


Attempting to play with ggplot

```{r}
xgrp <- ggplot(def, aes(def$m250, def$m500, def$m750)) + 
  geom_histogram()
  
  
  xgrp
```

I do not understand ggplot syntax.  Using the regular plot commands outlined [here](https://www.r-bloggers.com/overlapping-histogram-in-r/).  

```{r}
yyy <- rnorm(4000,4)
str(yyy)
```

```{r}
hist(def$m250, col=rgb(1,0,0,0.5))
hist(def$m500, col=rgb(0,0,1,0.5), add=T)
box()
```
Cool!

Just would have to figure out how to add a legend labelling the samples appropriately.  ALSO have to rescale in a metric that reflects the population mean.  How about raw deviation from the population mean?  

```{r}
hist(def$m250, col="lightblue")
hist(def$m500, col="red", add=T)
hist(def$m750, col="yellow", add=T)
box()


```

OK Let's write it up and send over to Steve.  Main title:  "Distribution of 1000 sample means for population size 4,000"

X-AXIS LABEL:  Sample mean (0 = population mean, 1 = 1 SD from population mean)
Y-AXIS LABEL:  Number of samples

[Very last example on this page](http://stackoverflow.com/questions/33480500/is-there-a-way-to-show-overlapping-histograms-in-r-without-adjusting-transparenc) might have a solution to the alpha problem using ggplot.  

```{r}
qplot(def$m250, fill=I('blue')) +
  geom_histogram(aes(def$m500), fill=I('green')) +
  geom_histogram(aes(def$m750), fill=I('red'),alpha=0.4)
```

This ggplot shit looks like crap.

```{r}

hist(def$m250, col="lightblue")
hist(def$m500, col="red", add=T)
hist(def$m750, col="yellow", add=T)
legend("topright",c("n=250","n=500","n=750"), col=c("lightblue","red","yellow"),lwd=10)
box()


```

cool!  Looks like the lwd command added the colors to the legend - or allowed legend to be large enough to show colors.  


```{r}

hist(def$m250, col="lightblue", 
  xlab="Sample mean (0 = pop. mean, 1 = pop. SD)",
  ylab="Number of samples", 
  main="Three distributions of 1000 sample means for population size 4,000")
hist(def$m500, col="red", add=T)
hist(def$m750, col="yellow", add=T)
legend("topright",c("n=250","n=500","n=750"), col=c("lightblue","red","yellow"),lwd=10)
box()


```

Conclusions?  A sample size of 250 yields a sample mean within 1/10th of an sd of the population mean in either direction over 97% of the time.  Greater sample sizes offer increased precision, but at a point of somewhat diminishing returns somewhere between n=250 and n=500.   


Let's see what 375 yields.

```{r}
def$m375 <-  msample(population,1000,350)
hist(def$m250, col="lightblue", 
  xlab="Sample mean",
  ylab="Number of samples", 
  main="Three distributions of 1000 sample means for \n population size 4,000 (M=0, SD=1)")
hist(def$m375, col="purple", add=T, density=20, angle=-75)
hist(def$m500, col="red", add=T)
hist(def$m750, col="yellow", add=T, density=10)
legend("topright",c("n=250","n=375","n=500","n=750"), col=c("lightblue","purple","red","yellow"),lwd=10)
box()

```
Interesting, going from 200 to 375 helps but not that much.  The jump to 500 appears to make a good chunk of difference.  
